%!TEX root = ../main.tex

\begin{abstract}
We study new candidates for symmetric cryptographic primitives that leverage alternation between linear functions over $\Z_2$ and $\Z_3$ to support fast protocols for secure multiparty computation (MPC). This continues the study of weak pseudorandom functions of this kind initiated by Boneh et al.\ (TCC 2018) and Cheon et al.\ (ePrint 2020).

We make the following contributions. 
\begin{itemize}
\item {\bf Candidates.} We propose new designs of symmetric primitives based on alternating moduli. These include candidate one-way functions, pseudorandom generators, and weak pseudorandom functions in which the key, the  input and the output are all over $\Z_2$. We propose concrete parameters based on cryptanalysis. 
\item {\bf Protocols.} We provide a unified approach for securely evaluating modulus-alternating primitives in different MPC models. For the original candidate of Boneh et al., our protocols obtain roughly 2x improvement in all performance measures. We report efficiency benchmarks of an optimized implementation.
\item {\bf Applications.} We showcase the usefulness of our candidates for a variety of applications. This includes short ``Picnic-style'' signature schemes, as well as protocols for oblivious pseudorandom functions, hierarchical key derivation, and distributed key generation for function secret sharing.
\end{itemize}



\end{abstract}

\input{Sections/introduction}
\input{Sections/preliminaries}
\input{Sections/core_primitives}
\input{Sections/cryptanalysis2}
\input{Sections/distributed_protocols}
\input{Sections/applications}
\input{Sections/evaluation}
\printbibliography

\iffull\else
\appendix
\newpage
\section*{SUPPLEMENTARY MATERIAL}
\input{Sections/appendix}
\fi